R Notebook

### 2019-10-01 src/AO_NAO_comparison.Rmd
i hate R

```{r}
naoraw <- read.csv("../data/env/nao_pc_monthlyX.csv", header = FALSE) 
head(naoraw)
```

lets give some column names. col 1  year, 2:13 are the months
```{r}
colnames(naoraw) <- c("year","Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "yr_t")
head(naoraw)
```

>>>>

```{r}
naoraw <- read.csv("../data/env/nao_pc_monthly.csv", header = FALSE) 
head(naoraw)
```

lets give some column names. col 1  year, 2:13 are the months
```{r}
colnames(naoraw) <- c("year","Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")
head(naoraw)
```

### 2019-10-01 src/plots for paper.Rmd
i hate R

```{r}
a <- ggplot(data = meddf) + geom_point(aes(y = layer, x = median, colour = month))
a
```

>>>>

```{r}
a <- ggplot(data = meddf) + geom_point(aes(y = layer, x = median, colour = month))
a

```{r get max probability for each depth}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

meddf <- data.frame(matrix(ncol = 3, nrow = 490))
colnames(meddf) <- c("layer", "month", "max")
r <- 1

for (m in 1:length(mthord)){
  mth <- mthord[m]
  mthlst <- list.files(paste0("../output/maxent/predictions/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  rstk <- stack(mthlst)
  rsum <- summary(rstk, na.rm = TRUE)
  rsum <- rsum["Max.", ]
  for (l in 1:length(rsum)){
    meddf$max[r] <- rsum[l]
    meddf$month[r] <- mth
    meddf$layer[r] <- names(rstk[[l]])
    r <- r+1
  }
}

meddf$layer <- gsub("avg_cloglog_", "", x = meddf$layer)
meddf$layer <- as.numeric(meddf$layer)
meddf <- meddf[order(meddf$layer), ]

write.csv(meddf, paste0("../output/maxent/paper_plots/med_data/max.csv"), row.names = FALSE)
```

```{r}
a <- ggplot(data = meddf) + geom_point(aes(y = layer, x = max, colour = month))
a
```

#Histograms of probability by depth

count number of cells that are not NA in each raster layer that are inside the mcp

```{r}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

clogasc_list <- list.files(paste0("../output/maxent/predictions/nov"), pattern = "^avg_cloglog_.*.asc", full.names = TRUE) #just choose a random month to calculate cells
cumst <- data.frame(0, 0)
colnames(cumst) <- c("depth", "no_cells")
for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumst[cum, 1] <- str_sub(ascname, 13)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  ccnt <- freq(cumasc, useNA='no')
  ccnt <- sum(ccnt[ ,2])
  cumst[cum, 2] <- ccnt
}

cumst$depth <- as.numeric(cumst$depth)
cumst1 <- cumst[order(cumst$no_cells), ]

write.csv(cumst1, "../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", row.names = FALSE)

first bin the probabilities for cells inside the mcp
```{r bin probabilities}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  clogasc_list <- list.files(paste0("../output/maxent/predictions/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)

  binprob <- function(x){
    ifelse(x > 0 & x < 0.1, 0.1,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.1 & x < 0.2, 0.2,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.2 & x < 0.3, 0.3,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.3 & x < 0.4, 0.4,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.4 & x < 0.5, 0.5,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.5 & x < 0.6, 0.6,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_6_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_6_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.6 & x < 0.7, 0.7,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_7_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_7_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.7 & x < 0.8, 0.8,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_8_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_8_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.8 & x < 0.9, 0.9,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_9_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_9_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

  binprob <- function(x){
    ifelse(x >= 0.9 & x <= 1, 1,
    ifelse(x <= 0, 0, NA))
  }

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_10_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_10_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}
```

get data to plot probability by depth... need to do manually 1-10
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec") 
binlst <- c(1:10)

binprob <- function(x){
  ifelse(x >0,  1,
  ifelse(x == -9999, 0, NA))
}

for (m in 1:length(mthord)){
  for (b in 1:length(binlst)){
  mth <- mthord[m]
  bin <- binlst[b]
  ascdepth <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_binned_", bin, "_.*asc"), full.names = TRUE)

  binaryavgstack <- stack(ascdepth)
  stackstathigh <- data.frame(matrix(ncol = 2, nrow = nlayers(binaryavgstack)))
  stackstathigh[ ,1] <- c(1:49)
  colnames(stackstathigh) <- c("asclayer", "prob_bin")

  for (lyr in 1:nlayers(binaryavgstack)){
    ascname <-  str_sub(ascdepth[lyr], 63, -5)
    dlay <- binaryavgstack[[lyr]]
    dlay <- calc(dlay, fun = binprob) #creates raster layer with cell values based on the binprob function
    lyrsum <- cellStats(dlay, sum)
    stackstathigh$prob_bin[lyr] <- lyrsum
    stackstathigh$asclayer[lyr] <- ascname

  }
  write.csv(stackstathigh, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_probbin_", bin, "_cellcount_bydepth_avg.csv"), row.names = FALSE)
  }
}

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  probblst <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, ".*probbin_.*.csv"), full.names = TRUE)
  a <- read.csv(probblst[1])
  b <- read.csv(probblst[2])
  c <- read.csv(probblst[3])
  d <- read.csv(probblst[4])
  e <- read.csv(probblst[5])
  f <- read.csv(probblst[6])
  g <- read.csv(probblst[7])
  h <- read.csv(probblst[8])
  i <- read.csv(probblst[9])
  j <- read.csv(probblst[10])

  stackstat <- cbind(a, b[ ,2], c[ ,2], d[ ,2], e[ , 2], f[ ,2], g[ ,2], h[ ,2], i[ ,2], j[ ,2])
  colnames(stackstat) <- c("depth", "0 - 0.09", "0.1 - 0.19", "0.2 - 0.29", "0.3 - 0.39", "0.4 - 0.49", "0.5 - 0.59", "0.6 - 0.69", "0.7 - 0.79", "0.8 - 0.89", ">0.9")
  stackstat <- melt(stackstat, id = "depth")
  stackstat <- stackstat[!(stackstat$depth == "1151.99"), ]
  stackstat <- stackstat[!(stackstat$depth == "1265.86"), ]
  stackstat <- stackstat[!(stackstat$depth == "1387.38"), ]

  colnames(stackstat) <- c("Depth", "Probability", "Cells")

  write.csv(stackstat, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_allprobbin_cellcount_bydepth_avg.csv"), row.names = FALSE)
}

think about how to get proportions...

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)

for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_allprobbin_cellcount_bydepth_avg.csv"), header = TRUE, stringsAsFactors=FALSE)
  for (r in 1:nrow(a)){
    a$Depth[r] <- gsub("b_avg_cloglog_", "", x = a$Depth[r])
    d1 <- str_sub(a$Depth[r], end = 4)
	  for (ro in 1:nrow(cumst1)){
      d2 <- str_sub(cumst1$depth[ro], end = 4)
      if (d1 == d2){
          a$total_cells[r] <- cumst1$no_cells[ro]
      }
	  }
    a$p_cells[r] <- (a$Cells[r]/a$total_cells[r])*100
  }
    a$Depth <- as.numeric(a$Depth)

  write.csv(a, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), row.names = FALSE)
}

histogram of probability by depth - by proportion

```{r}

bydepth <- ggplot(a, aes(Depth, p_cells, fill = Probability)) + geom_col() + scale_x_reverse() + coord_flip() #XXXXXcareful - the deeper layers aren't being displayed correctly here
plot(bydepth)
#png(paste0("../output/maxent/predictions/", mthna, "/depthplot_probavg_prop.png"))
#print(bydepth)
#dev.off()
```

ok lets try colour the probabilites to match the maps...

```{r}
probcol <- rev(brewer.pal(10,"RdYlGn"))
bydepth <- ggplot(a, aes(Depth, p_cells, fill = Probability)) + geom_col() + scale_x_reverse() + coord_flip() + scale_fill_manual(values = probcol) #XXXXXcareful - the deeper layers aren't being displayed correctly here
plot(bydepth)
```

ok now lets lump all the 0.39 and under together...

```{r}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

binprob <- function(x){
    ifelse(x > 0 & x <0.4, 1,
    ifelse(x <= 0, 0, NA))
}

for (m in 1:length(mthord)){
  mth <- "dec"
  clogasc_list <- list.files(paste0("../output/maxent/predictions/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    cumasc <- raster::mask(x = cumasc, mask = outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_binned_avgprob_", ascname, ".asc"), overwrite = TRUE)
    #plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_binned_avgprob_", ascname, ".png")), overwrite = TRUE)
    #dev.off() # stops automatic saving of the plot to a png
  }
}
```

get data to plot probability by depth... 
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  ascdepth <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_u0.4_binned_avgprob_", ".*asc"), full.names = TRUE)

  binaryavgstack <- stack(ascdepth)
  stackstathigh <- data.frame(matrix(ncol = 2, nrow = nlayers(binaryavgstack)))
  stackstathigh[ ,1] <- c(1:49)
  colnames(stackstathigh) <- c("asclayer", "prob_bin")

  for (lyr in 1:nlayers(binaryavgstack)){
    ascname <-  str_sub(ascdepth[lyr], 63, -5)
    dlay <- binaryavgstack[[lyr]]
    lyrsum <- cellStats(dlay, sum)
    stackstathigh$prob_bin[lyr] <- lyrsum
    stackstathigh$asclayer[lyr] <- ascname

  }
  write.csv(stackstathigh, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_probbin_cellcount_bydepth_avg.csv"), row.names = FALSE)
}

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  probblst <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_u0.4_probbin_cellcount_bydepth_avg.csv"), full.names = TRUE)
  stackstat <- read.csv(probblst[1])

  colnames(stackstat) <- c("depth", "0 - 0.39")
  stackstat <- melt(stackstat, id = "depth")
  stackstat <- stackstat[!(stackstat$depth == "1151.99"), ]
  stackstat <- stackstat[!(stackstat$depth == "1265.86"), ]
  stackstat <- stackstat[!(stackstat$depth == "1387.38"), ]

  colnames(stackstat) <- c("Depth", "Probability", "Cells")

  write.csv(stackstat, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_allprobbin_cellcount_bydepth_avg.csv"), row.names = FALSE)
}

get proportions...

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)

for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_allprobbin_cellcount_bydepth_avg.csv"), header = TRUE, stringsAsFactors=FALSE)
  for (r in 1:nrow(a)){
    a$Depth[r] <- gsub("prob_avg_cloglog_", "", x = a$Depth[r])
    d1 <- str_sub(a$Depth[r], end = 4)
	  for (ro in 1:nrow(cumst1)){
      d2 <- str_sub(cumst1$depth[ro], end = 4)
      if (d1 == d2){
          a$total_cells[r] <- cumst1$no_cells[ro]
      }
	  }
    a$p_cells[r] <- (a$Cells[r]/a$total_cells[r])*100
  }
   a$Depth <- as.numeric(a$Depth)

  write.csv(a, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_dis_prob_cells.csv"), row.names = FALSE)
}

merge the u0.4 dataset with the original
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  b <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  c <- rbind(a, b)
  c <- c[!(c$Probability == "0 - 0.09"), ]
  c <- c[!(c$Probability == "0.1 - 0.19"), ]
  c <- c[!(c$Probability == "0.2 - 0.29"), ]
  c <- c[!(c$Probability == "0.3 - 0.39"), ]
  write.csv(c, paste0("../output//maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"))
}
```

ok no try plot

```{r}
probcol <- rev(brewer.pal(7,"RdYlGn"))
bydepth <- ggplot(c, aes(Depth, p_cells, fill = Probability)) + geom_col() + scale_x_reverse() + coord_flip() + scale_fill_manual(values = probcol) #XXXXXcareful - the deeper layers aren't being displayed correctly here
plot(bydepth)
```

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)
for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE)
  head(a)
  d <- unique(a$Depth)
  x <- data.frame(matrix(nrow = length(d)))
  for (s in 1:length(d)){
    dep <- d[s]
    sd <- subset(a, Depth == dep)
    sd <- subset(sd, Probability == "0 - 0.09"| Probability == "0.1 - 0.19"| Probability == "0.2 - 0.29"| Probability == "0.3 - 0.39")
    c <- sum(sd$Cells)
    x$Depth[s] <- dep
    x$Probability[s] <- "0 - 0.39"
    x$cells[s] <- c
    x$p_cells[s] <- 1
  }
  x <- subset(x, select = -c(matrix.nrow...length.d..))
  x$cells[is.na(x$cells)] <- 0
  # for (r in 1:nrow(x)){
  #   d1 <- str_sub(x$Depth[r], end = 4)
  #   for (ro in 1:nrow(cumst1)){
  #     d2 <- str_sub(cumst1$depth[ro], end = 4)
  #     if (d1 == d2){
  #         x$total_cells[r] <- cumst1$no_cells[ro]
  #     }
  #   }
  # }
  # for (r in 1:nrow(x)){
  #    x$p_cells[r] <- (x$Cells[r]/x$total_cells[r])*100

 # }

  write.csv(x, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"))
}
```

merge the u0.4 dataset with the original
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  b <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE, stringsAsFactors=FALSE)
  c <- rbind(a, b)
  c <- c[!(c$Probability == "0 - 0.09"), ]
  c <- c[!(c$Probability == "0.1 - 0.19"), ]
  c <- c[!(c$Probability == "0.2 - 0.29"), ]
  c <- c[!(c$Probability == "0.3 - 0.39"), ]
  write.csv(c, paste0("../output//maxent/paper_plots/prob_by_depth/", mth, "_u0.4s_dis_prob_cells.csv"))
}
```

```{r}
probcol <- rev(brewer.pal(7,"RdYlGn"))
bydepth <- ggplot(c, aes(Depth, p_cells, fill = Probability)) + geom_col() + scale_x_reverse() + coord_flip() + scale_fill_manual(values = probcol) #XXXXXcareful - the deeper layers aren't being displayed correctly here
plot(bydepth)
```

ok dont forget the colours will need to match the maps so you may need to manually create your own list for whatever scheme you choose...

now MJ suggested to only show some depths (the most commonly predicted ones)

ok lets try get an probability for the whole month

```{r}
a <- read.csv("../output/maxent/predictions/jul/dis_prob_cells.csv", header = TRUE)

#subset the probability ranges
p1 <- subset(a, Probability == "0 - 0.09")
p2 <- subset(a, Probability == "0.1 - 0.19")
p3 <- subset(a, Probability == "0.2 - 0.29")
p4 <- subset(a, Probability == "0.3 - 0.39")
p5 <- subset(a, Probability == "0.4 - 0.49")
p6 <- subset(a, Probability == "0.5 - 0.59")
p7 <- subset(a, Probability == "0.6 - 0.69")
p8 <- subset(a, Probability == "0.7 - 0.79")
p9 <- subset(a, Probability == "0.8 - 0.89")
p10 <- subset(a, Probability == ">0.9")

#count the number of cells per probability.

cp1 <- sum(p1$Cells)
cp2 <- sum(p2$Cells)
cp3 <- sum(p3$Cells)
cp4 <- sum(p4$Cells)
cp5 <- sum(p5$Cells)
cp6 <- sum(p6$Cells)
cp7 <- sum(p7$Cells)
cp8 <- sum(p8$Cells)
cp9 <- sum(p9$Cells)
cp10 <- sum(p10$Cells)

tc2 <- sum(cp1, cp2, cp3, cp4, cp5, cp6, cp7, cp8, cp9, cp10) #how many cells in total for novy have a value
tcell <- sum(p1$total_cells) # how many cells are available to have a value...
#tc2 and tcell should match

#create datbase of total cells per probability bin for the month

b <- unique(a$Probability) #get the unique probability bins
c <- as.data.frame(rbind(cp1, cp2,  cp3, cp4, cp5, cp6, cp7, cp8, cp9, cp10))
c$probability <- b
colnames(c) <- c("cells", "prob_bin")
rownames(c) <- c()
c$month <- "jul"
```

make plot of probability over the month
```{r}
pmth <- ggplot(d, aes(month, cells, fill = prob_bin)) + geom_bar(stat='identity') 
plot(pmth)
png(paste0("../output/maxent/predictions/", mthna, "/prob_avg_mth.png"))
print(pmth)
dev.off()
```

merge two months of data together into one file then plot

```{r}
f <- rbind(c, d)
pmth <- ggplot(f, aes(month, cells, fill = prob_bin)) + geom_bar(stat='identity') 
plot(pmth)
png(paste0("../output/maxent/predictions/prob_avg_mth_test.png"))
print(pmth)
dev.off()
```

### 2019-10-01 src/testing_file.Rmd
i hate R

aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/predictions/may", pattern = "^avg_clog.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
brk <- seq(0, 1, 0.1) #for legend
lgc <- sequential_hcl(10, palette = "YlOrRd") #colour scheme from colorspace package
redtrans <- rgb(218, 215, 216, 120, maxColorValue=255) #mcp
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

pras6 <- raster(maplst[37])
pras180 <- raster(maplst[14])
pras370 <- raster(maplst[28])
pras697 <- raster(maplst[41])
crs(pras6) <- apr
crs(pras180) <- apr
crs(pras370) <- apr
crs(pras697) <- apr
ascname6 <- names(pras6)
ascname180 <- names(pras180)
ascname370 <- names(pras370)
ascname697 <- names(pras697)
pstack <- stack(pras6, pras180, pras370, pras697) #stack the layers

pras1 <- raster(maplst[1])
pras2 <- raster(maplst[2])
pras3 <- raster(maplst[3])
pras4 <- raster(maplst[4])
crs(pras1) <- apr
crs(pras2) <- apr
crs(pras3) <- apr
crs(pras4) <- apr

pstack <- stack(pras6, pras180, pras370, pras697, pras1, pras2, pras3, pras4) #stack the layers

cls <- c("6m", "180m", "370m", "697m")
rws <- c("may", "dummy")
mapTheme <- rasterTheme(region = rev(brewer.pal(10,"RdYlGn")))
my.at <- seq(0, 1, by = 0.1)

@@

dev.copy(png, (paste0("../output/maxent/predictions/testplots/rasterVis.png")), width = 1920,height = 1080)
dev.off() # stops automatic saving of the plot to a png))

>>>>

aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/predictions/may", pattern = "^avg_clog.*.asc", full.names = TRUE)
maplst2 <- list.files("../output/maxent/predictions/sep", pattern = "^avg_clog.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
brk <- seq(0, 1, 0.1) #for legend
lgc <- sequential_hcl(10, palette = "YlOrRd") #colour scheme from colorspace package
redtrans <- rgb(218, 215, 216, 120, maxColorValue=255) #mcp
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

pras6 <- raster(maplst[37])
pras180 <- raster(maplst[14])
pras370 <- raster(maplst[28])
pras697 <- raster(maplst[41])
p2ras6 <- raster(maplst2[37])
p2ras180 <- raster(maplst2[14])
p2ras370 <- raster(maplst2[28])
p2ras697 <- raster(maplst2[41])
crs(pras6) <- apr
crs(pras180) <- apr
crs(pras370) <- apr
crs(pras697) <- apr
crs(p2ras6) <- apr
crs(p2ras180) <- apr
crs(p2ras370) <- apr
crs(p2ras697) <- apr
ascname6 <- names(pras6)
ascname180 <- names(pras180)
ascname370 <- names(pras370)
ascname697 <- names(pras697)
a2scname6 <- names(p2ras6)
a2scname180 <- names(p2ras180)
a2scname370 <- names(p2ras370)
a2scname697 <- names(p2ras697)

# pstack <- stack(pras6, pras180, pras370, pras697) #stack the layers
# 
# pras1 <- raster(maplst[1])
# pras2 <- raster(maplst[2])
# pras3 <- raster(maplst[3])
# pras4 <- raster(maplst[4])
# crs(pras1) <- apr
# crs(pras2) <- apr
# crs(pras3) <- apr
# crs(pras4) <- apr

pstack <- stack(pras6, pras180, pras370, pras697, p2ras6, p2ras180, p2ras370, p2ras697) #stack the layers

cls <- c("6m", "180m", "370m", "697m")
rws <- c("May", "Sep")
mapTheme <- rasterTheme(region = rev(brewer.pal(10,"RdYlGn")))
my.at <- seq(0, 1, by = 0.1)

@@

#dev.copy(png, (paste0("../output/maxent/predictions/testplots/rasterVis.png")), width = 1920,height = 1080)
#dev.off() # stops automatic saving of the plot to a png))
